Master's Project Journal

### 2018-11-14 tex_files/Journal.tex
same date part 2

\section*{Basic Measurements}
Lock range at bias of 82:
$$4.19\rightarrow12.34\textrm{ MHz} $$ 
Capture range at bias of 82:
$$4.25\rightarrow12.76\textrm{ MHz}  $$
Jitter at bias of 82:\\
%TODO
Jitter locked to 5~ MHz:\\
%TODO
Frequency sensitivity(control code to output):
$$ 258\times10^6\frac{1}{2^{12}}=62.988\textrm{ MHz} $$
Overall proportional gain (time $\rightarrow$ TDC $\rightarrow$ frequency):
$$ 8.998 \textrm{ KHz/degree} $$
LPF cutoff:\\

>>>>

\section*{Basic Measurements}
Lock range at bias of 82:
$$4.19\rightarrow12.34\textrm{ MHz} $$ 
Capture range at bias of 82:
$$4.25\rightarrow12.76\textrm{ MHz}  $$
Jitter at bias of 82:\\
$$ 200.1665\pm1.9689\textrm{ nsec} $$
Jitter locked to 5~ MHz:\\
$$ 200.009\pm2.7378\textrm{ nsec} $$
Frequency sensitivity(control code to output):
$$ 258\times10^6\frac{1}{2^{12}}=62.988\textrm{ MHz} $$
Overall proportional gain (time $\rightarrow$ TDC $\rightarrow$ frequency):
$$ 8.998 \textrm{ KHz/degree} $$
LPF cutoff:\\
